\section{Overview}

The necessity and requirements of different kinds of artificially intelligent robots are increasing day by day in the modern world. The latest innovations in technology are making it possible for us to further develop in different areas of human life. One of such up and rising sectors is the robotic industry. 

In the world of robots, quadrupeds, or robots with 4 legs, are best equipped with the ability to maneuver complex terrain much faster and with enhanced stability. It follows the gait patterns of animals and are versatile in locomotion and movement. That is the major intent behind the development of these kinds of robots by the academia, companies, and robot enthusiasts around the world.

Mobile robots like quadrupeds have extensive applications and the potential to be one of the most important innovations in the future of technology. Quadruped robots are superior in ability when commpared with wheeled and tracked robots due to its potential to explore in highly variable terrain like humans and animals. It also provides much more stability than a humanoid robots because of its 4 legged from that enables it to exploit the advantages of legged locomotion. The dynamic range of feet placement extends the reach and limits the constraints on directional movement. In addition to this, the low center of gravity accounts for enhanced balance and stability preventing the robot from toppling over in difficult circumstances, hence reducing damage and failure of the robot in operation. Considering the dynamic and stable capabilities of a quadruped robot, we have taken inspiration from the immaculate development in the realm of quadruped robots and have tried to create one of our own.

The robot works with information from stereo cam setups, LiDAR data and even auxiliary sensors like ultrasonic range sensors for perception of the environment. The robot uses cheap, commercially available parts, and has been designed with modularity in mind.